Etox-Base: A tool to derive exposure endpoints from chemical test results

### 2019-10-14 article/parts/04_technical_validation.tex
Updates from Overleaf

>>>>

\begin{figure}
    \includegraphics[width=1\linewidth]{article/figures/Standartox_PPDB.png}
    \caption{
        Comparison between Standartox and PPDB values
    }
    \label{fig:standartox_ppdb_diff}
\end{figure}

In order to validate \standartox we compared resulting values with values from other data bases, such as the PPDB. Of 542 chemicals, only 16\% diverged from the PPDB values by a factor greater than 10, supporting plausibility of the \standartox results \ref{fig:standartox_ppdb_diff}.
